### 2023-10-06 chapters/paper_review/04_benchmarking.tex
Improve hyphenation and add "= for compound words

\section{Benchmarks for self-supervised learning}
\label{section:benchmark}

@@

\subsection{Datasets only for pre-training} 
\Cref{table:datasets} summarizes datasets used for pre-training SSL techniques
in the literature. These datasets are usually large but with limited or no
labels. Libri-light (LL)~\parencite{kahn_libri-light_2020}, one of these datasets, is
derived from audiobooks that are part of the
LibriVox\footnote{https://librivox.org/ \label{librivox}} project. LL contains
60k hours of spoken English audio tagged with SNR, speaker ID, and genre
descriptions. The speech examples in Audioset~\parencite{gemmeke_audio_2017}, which
consists of over 2M 10-second YouTube video clips human-annotated with 632
audio events, have also been used for pre-training. Audioset has 2.5k hours
of audio of varying quality, different languages, and sometimes multiple sound
sources. AVSpeech~\parencite{ephrat_looking_2018} is another large-scale audio-visual
dataset used in SSL research, comprising 4.7k hours of clips from a wide
variety of languages. 
Each clip contains a visible face and audible sound originating from a single
speaker without interfering background signals. The 3100-hour audio part of
AVSpeech has been used to learn audio-only 
representations~\parencite{kawakami_learning_2020}. The Fisher corpus~\parencite{cieri_fisher_2004} collects
over 2k hours of conversational telephone speech, 1k hours of which is utilized
for pre-training~\parencite{jiang_further_2021}. Industrial researchers have also
begun to build large-scale datasets for learning speech representations.
For instance, 10k hours of real-world far-field English voice commands for
self-supervised pre-training have been collected at 
Amazon~\parencite{sadhu_wav2vecc_2021}.

In addition to these English and multilingual efforts, researchers have also
collected corpora for pre-training Chinese speech representations. Didi Dictation
and Didi Callcenter~\parencite{jiang_improving_2019, jiang_further_2021} are two
internal datasets containing respectively 10k hours of read speech collected
from mobile dictation application and 10k hours of spontaneous phone calls
between users and customer service staff.

\subsection{Datasets for both pre-training and evaluation}\label{sec:datasets}
Several datasets that provide both speech and associated transcripts and
speaker labels have also been used to develop SSL techniques by enabling
in-domain pre-training and evaluation. Such datasets are also listed in
\cref{table:datasets}. One of the most commonly used datasets in this category
is LibriSpeech (LS)~\parencite{panayotov_librispeech_2015}, a labeled corpus
containing 960 hours of
read English speech, which is also derived from an open-source audiobooks
project.\textsuperscript{\ref{librivox}} The corpus consists of subsets
\textit{train-clean-100}, \textit{train-clean-360}, \textit{train-other-500},
\textit{dev-clean}, \textit{dev-other}, \textit{test-clean}, and
\textit{test-other} used for training, development, and testing, respectively.
Subsets tagged with \textit{other} are more challenging utterances from
speakers that yield higher WER as measured with previously built models. LS is
used for unsupervised representation pre-training by ignoring its labels, and
can also be utilized to evaluate the performance of representation on ASR, phoneme recognition (PR),
phoneme classification (PC), and speaker identification (SID) tasks. Wall Street Journal (WSJ)~\parencite{paul_design_1992} is another
widely adopted, labeled corpus for pre-training. Its labels can evaluate
performance for ASR, PR, PC, and SID. The original WSJ corpus contains 400 hours
of English read speech data, and today its \textit{si284} (81 hours),
\textit{dev93}, \textit{eval92} subsets are the most-used partitions for
unsupervised training, development, and test, respectively.  The \textit{si84}
(15 hours) partition is also used for training.

The speech community also utilizes multilingual corpora. These are often
large-scale, which facilitates pre-training, but are also partially labeled for ASR
evaluation (PC and PR can be enabled via phone-level forced alignment). These
corpora include Common Voice (CV)~\parencite{ardila_common_2020}, Multilingual
LibriSpeech (MLS)~\parencite{pratap_mls_2020}, VoxPopuli 
(VP)~\parencite{wang_voxpopuli_2021}, and BABEL (BBL)~\parencite{gales_speech_2014}. CV is
an open-source, multi-language, growing dataset of voices containing 11k hours
of audio from 76 languages as of the date this review was written (Common Voice
corpus~7.0). Researchers usually use part of this for pre-training (e.g., 7k
hours/60 languages in \parencite{babu_xlsr_2021} and 430 hours/29 languages in
\parencite{kawakami_learning_2020}) or evaluation. 
MLS derives content from read audiobooks of LibriVox and contains data in eight
European languages for a total of 50k hours of audio. VP comprises a total of 400k
hours of parliamentary speech from the European parliament in 23 European
languages.
The entire dataset~\parencite{babu_xlsr_2021} or a 24k-hour 
portion~\parencite{chen_unispeechsat_2021, chen_wavlm_2021} thereof has been used for pre-training. BBL
consists of 1k hours of conversational telephone speech in 17 African and Asian
languages.

Several datasets, including GigaSpeech~\parencite{chen_gigaspeech_2021}, TED-LIUM~3
(TED3)~\parencite{hernandez_tedlium_2018}, TED-LIUM~2 (TED2)~\parencite{rousseau_tedlium_2012},
Switchboard (SWB)~\parencite{godfrey_switchboard_1992}, 
TIMIT~\parencite{garofolo_timit_1993}, and VoxLingua107 \parencite{valk_voxlingua107_2021}, are
labeled and conventionally used for evaluation, while their audio streams are
also aggregated to build diversified and large-scale corpora for unsupervised
pre-training~\parencite{kawakami_learning_2020, song_speechxlnet_2020, babu_xlsr_2021}.
GigaSpeech is a multi-domain English ASR corpus with 33k hours of audio
collected from audiobooks, podcasts, and YouTube. A subset of 10k audio is
transcribed. TED2 comes with 118 hours of English speech extracted from
TED conference talks and its transcription for evaluating ASR. Its recordings
are clear but with some reverberation. TED3 is an extension of TED2 and
comprises 450 hours of talks. SWB is a 260-hour conversational speech
recognition dataset containing two-sided telephone conversations.
The TIMIT corpus was designed to provide read speech data and its word and
phone-level transcriptions for acoustic-phonetic studies. It contains recordings
in American English. Compared to the previous corpora labeled for ASR
evaluation, VoxLingua107 consists of 6.6k hours of audio in 107 languages and
is annotated for language identification. Beyond the original purpose of
evaluation, these corpora are also used in pre-training to improve the
generalizability of learned representations.

For the purpose of pre-training and evaluating Mandarin speech representations,
the authors of \parencite{jiang_improving_2019, jiang_further_2021} also compiled Open Mandarin, 
an open-source Mandarin dataset of 1.5k hours of speech from
the Linguistic Data Consortium (LDC) and
OpenSLR.\footnote{\url{https://openslr.org}} Open Mandarin consists of the HKUST
Mandarin Telephone Speech Corpus (HKUST, 200 hours of spontaneous 
speech, of which
168 hours of audio is used for pre-training; the development and test sets are
excluded.)~\parencite{liu_hkust_2006}, AISHELL-1~\parencite{bu_aishell1_2017} (178 hours of
read speech),
aidatatang 200zh (200 hours, read speech)~\parencite{beijingdatatangtechnologycoltd_aidatatang_}, MAGICDATA
Mandarin Chinese Read Speech Corpus (755 hours, read speech)~\parencite{magicdatatechnologycoltd_magicdata_2019},
Free ST Chinese Mandarin Corpus (ST-CMDS, 100 hours, read speech)~\parencite{surfingtechcoltd_stcmds_},
and Primewords Chinese Corpus Set 1 (100 hours, read speech)~\parencite{primewordsinformationtechnologycoltd_primewords_2018}. 
Both HKUST and AISHELL-1 are labeled and are suitable for ASR evaluation.

@@

Besides the aforementioned datasets, conventional speech processing benchmarks
are also used to evaluate self-supervised representations. Studies leverage Hub5,
DIRHA, and CHiME-5 to measure the efficacy of representations in ASR.
The Hub5 evaluation (LDC2002T43 and LDC2002S09, also referred to as the NIST 2000
Hub5 English evaluation set) contains 40 transcribed English telephone
conversations only for testing, where 20 are from conversations collected in
SWB studies but not released with the SWB dataset, and the rest are from CallHome
American English Speech (LDC97S42). DIRHA~\parencite{ravanelli_dirhaenglish_2015}, short for
Distant-speech Interaction for Robust Home Applications, is a database composed
of utterances sampled from WSJ, speech of keywords and commands, and
phonetically-rich sentences. These utterances are read by UK and US English
speakers and recorded with microphone arrays. CHiME-5~\parencite{barker_fifth_2018} is
a challenge that aims to advance robust ASR and presents a dataset of natural
conversational speech collected under a dinner party scenario with microphone
arrays. A team at Amazon Alexa also recorded and transcribed a corpus of 1k
hours of audio for model training and evaluation~\parencite{sadhu_wav2vecc_2021}.

@@

Last, \parencite{tagliasacchi_pretraining_2020} puts together five datasets 
(MUSAN~\parencite{snyder_musan_2015}, Bird Audio Detection~\parencite{stowell_automatic_2019},
Speech Commands~\parencite{warden_speech_2018}, Spoken Language 
Identification~\parencite{oponowicz_spoken_2018}, and TUT Urban Acoustic Scenes 2018~\parencite{mesaros_detection_2018}) plus
an SID task built with the LS \textit{train-clean-100} subset to evaluate the
capability of representations on audio event detection.
\parencite{quitry_learning_2019} employs the NSynth dataset~\parencite{engel_neural_2017} on top
of the six for benchmarking. As many of the datasets are built for research in
audio processing, we here provide only a list of these datasets for reference.

\begin{table*}[t]
  \centering
  \scriptsize %footnotesize %small, scriptsize, tiny
  \caption[Summary of datasets used for pre-training or evaluation of SSL techniques in the literature.]%
  {Summary of datasets used for pre-training (denoted as PT) or
  evaluation (denoted as EV) of SSL techniques in the literature. The languages and
  sizes of the datasets are provided in columns 3 and 4. Column 5 lists the tasks each
  dataset is used to evaluate. Abbrevations are listed in \cref{footnote:table:datasets-abbrevations}.}
  \label{table:datasets}
  \resizebox*{0.99\textwidth}{!}{%
  {\renewcommand*\arraystretch{1.2}
  \begin{tabular}{llllll}
    \toprule
    Dataset & Purpose & Lang. & Size [hours] & Task & License \\
    \midrule
    LibriLight (LL) & PT & EN & 60k & - & MIT License \\ \hline
    AudioSet & PT & Multi & 2.5k & - & CC BY 4.0 \\ \hline %Bidir-CPC, Audio2Vec
    AVSpeech & PT & Multi & 3.1k & - & CC BY 4.0 \\ \hline %Bidir-CPC
    Fisher & PT & EN & 2k/1k \parencite{jiang_further_2021}  & - & Linguistic Data Consortium (LDC) \\ \hline % MPC

@@

    \multirow{2}{*}{Work} & \multirow{2}{*}{\makecell[l]{Pre-training\\ corpus}} & \multirow{2}{*}{Task} & \multicolumn{2}{c}{Dataset} & \multirow{2}{*}{Transfer} & \multirow{2}{*}{Fine-tuning labels used} \\ \cline{4-5}

@@

\addtocounter{footnote}{1}
\footnotetext{\label{footnote:table:method_data_setting}
  The \textbf{Pre-training corpus}, \textbf{Fine-tuning}, and
  \textbf{Test} columns list the datasets used in each work, and the \textbf{Task}
  column lists the tasks performed in the corresponding papers. 
  The \textbf{Transfer} column indicates whether the SSL technique is evaluated by its capability for
  transfer learning, i.e., different datasets are utilized for pre-training and
  fine-tuning. The \textbf{Fine-tuning labels used} column summarizes the
  amount of labeled examples used in downstream fine-tuning.
}

@@

\addtocounter{footnote}{1}
\footnotetext{\label{footnote:AED-datasets}
The 6 AED datasets used in
\parencite{tagliasacchi_pretraining_2020} are MUSAN~\parencite{snyder_musan_2015}, Bird Audio
Detection~\parencite{stowell_automatic_2019}, Speech Commands~\parencite{warden_speech_2018},
Spoken Language Identification~\parencite{oponowicz_spoken_2018}, TUT Urban Acoustic
Scenes 2018~\parencite{mesaros_detection_2018} plus an SID task built with LS
\textit{train-clean-100}. In addition to the 6 datasets,
\parencite{quitry_learning_2019} use the NSynth dataset~\parencite{engel_neural_2017} for
evaluation.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:CPC-8k}
A collection of AudioSet, AVSpeech,
CV-dataset, LS, WSJ, TIMIT, Speech Accent Archive 
(SSA)~\parencite{weinberger_speech_2011}, TED3, and SWB. SSA is a growing annotated corpus of
English speech with various accents. Among the papers studied in this review, SSA
is used in \parencite{kawakami_learning_2020} only for pre-training, and only 1 hour
of audio is utilized. Thus, we exclude it from our discussion in
\cref{section:benchmark}.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:low-resource}
A subset of the official training
split is sampled, usually to mimic low-resource learning conditions or to
quickly evaluate for training and testing on the same split but disjoint
subsets.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:APC-split}
Dataset split into training,
validation, and test subsets at a ratio of 8:1:1.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:91-split-dev}
Dataset split into training
and validation subsets at a ratio of 9:1.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:91-split-test}
The dataset split into training
and test subsets at a ratio of 9:1.}

\subsection{Experiment settings for evaluating SSL techniques}
A common way to benchmark SSL techniques and show their efficacy is to
fine-tune a pre-trained SSL model for a supervised downstream task.
Depending on the corpora used in pre-training and fine-tuning, techniques can
be benchmarked in terms of their capability to transfer knowledge across datasets
(i.e., using pre-training corpora that differ from the fine-tuning ones), their
benefit when training with limited labeled examples (i.e., sampling a subset of
labeled examples for fine-tuning), or their improvement over a fully supervised
baseline (i.e., using the entire training split of downstream datasets for
fine-tuning). \cref{table:method_data_setting,table:method_data_setting_2} summarize experiment settings used in the
SSL literature, including the pre-training corpora, downstream tasks and datasets,
and the amount of fine-tuning labels used, which indicates the targeted
benchmarking scenario as discussed above. Note that there are a variety of ways
to fine-tune pre-trained networks (e.g., fine-tune the entire network,
freeze certain layers during fine-tuning, and add various architectures of
prediction layers to pre-trained networks). We here omit
descriptions of these choices; readers can consult the
original publications for details.

As observed in \cref{table:method_data_setting,table:method_data_setting_2}, LS and WSJ are the most commonly used
pre-training corpora. At the same time, we observe a
growing industry investment in pre-training with larger datasets, e.g.,
CPC-8k (8k hours) for Bidir-CPC~\parencite{kawakami_learning_2020}, LL (60k hours) for
CPC modified~\parencite{riviere_unsupervised_2020}, 
wav2vec 2.0~\parencite{baevski_wav2vec_2020}, and HuBERT~\parencite{hsu_hubert_2021}, Alexa internal
datasets (10k hours) for wav2vec-c~\parencite{sadhu_wav2vecc_2021}, Didi internal
datasets (10k hours) for MPC~\parencite{jiang_improving_2019, jiang_further_2021}, the
combination of Gigaspeech, VP-24k, and LL (94k hours in total) for
UniSpeech-SAT~\parencite{chen_unispeechsat_2021} and WavLM~\parencite{chen_wavlm_2021}, and
the combination of VP-400K, MLS, CV-dataset, VL and BBL (436k hours in total)
for XLS-R~\parencite{babu_xlsr_2021}. We expect this trend to continue with the growth
in available computing power. Most studies focuses on learning representations
for English, whereas Chinese~\parencite{jiang_improving_2019, jiang_further_2021} and
multilinguality~\parencite{kawakami_learning_2020, babu_xlsr_2021} are also gaining
attention. Compared to pre-training, datasets used for fine-tuning are more
diverse and cover downstream tasks as varied as ASR, PR, PC, SID, AED,
Sentiment, ST, and LID. For benchmarking training scenarios covering full
supervision as well as limited resources, the amount of labeled examples used for
fine-tuning also varies from several minutes up to 1k hours. Recent
benchmarks such as SUPERB~\parencite{yang_superb_2021} that consolidate multiple 
downstream tasks have gained attention for evaluating SSL
methodologies~\parencite{chen_unispeechsat_2021, chen_wavlm_2021}. The goal of such benchmarks is
to provide a holistic evaluation of the performance of learned representations; 
we discuss these in detail in \cref{sec:benchmark}. With the increasing
popularity of SSL research, we expect future experiment settings to proliferate
and cover more languages, downstream tasks, and pre-training/fine-tuning
datasets.

>>>>

\section{Benchmarks for self"=supervised learning}
\label{section:benchmark}

@@

\subsection{Datasets only for pre"=training} 
\Cref{table:datasets} summarizes datasets used for pre"=training SSL techniques
in the literature. These datasets are usually large but with limited or no
labels. Libri-light (LL)~\parencite{kahn_libri-light_2020}, one of these datasets, is
derived from audiobooks that are part of the
LibriVox\footnote{https://librivox.org/ \label{librivox}} project. LL contains
60k hours of spoken English audio tagged with SNR, speaker ID, and genre
descriptions. The speech examples in Audioset~\parencite{gemmeke_audio_2017}, which
consists of over 2M 10-second YouTube video clips human-annotated with 632
audio events, have also been used for pre"=training. Audioset has 2.5k hours
of audio of varying quality, different languages, and sometimes multiple sound
sources. AVSpeech~\parencite{ephrat_looking_2018} is another large-scale audio-visual
dataset used in SSL research, comprising 4.7k hours of clips from a wide
variety of languages. 
Each clip contains a visible face and audible sound originating from a single
speaker without interfering background signals. The 3100-hour audio part of
AVSpeech has been used to learn audio-only 
representations~\parencite{kawakami_learning_2020}. The Fisher corpus~\parencite{cieri_fisher_2004} collects
over 2k hours of conversational telephone speech, 1k hours of which is utilized
for pre"=training~\parencite{jiang_further_2021}. Industrial researchers have also
begun to build large-scale datasets for learning speech representations.
For instance, 10k hours of real-world far-field English voice commands for
self"=supervised pre"=training have been collected at 
Amazon~\parencite{sadhu_wav2vecc_2021}.

In addition to these English and multilingual efforts, researchers have also
collected corpora for pre"=training Chinese speech representations. Didi Dictation
and Didi Callcenter~\parencite{jiang_improving_2019, jiang_further_2021} are two
internal datasets containing respectively 10k hours of read speech collected
from mobile dictation application and 10k hours of spontaneous phone calls
between users and customer service staff.

\subsection{Datasets for both pre"=training and evaluation}\label{sec:datasets}
Several datasets that provide both speech and associated transcripts and
speaker labels have also been used to develop SSL techniques by enabling
in-domain pre"=training and evaluation. Such datasets are also listed in
\cref{table:datasets}. One of the most commonly used datasets in this category
is LibriSpeech (LS)~\parencite{panayotov_librispeech_2015}, a labeled corpus
containing 960 hours of
read English speech, which is also derived from an open-source audiobooks
project.\textsuperscript{\ref{librivox}} The corpus consists of subsets
\textit{train-clean-100}, \textit{train-clean-360}, \textit{train-other-500},
\textit{dev-clean}, \textit{dev-other}, \textit{test-clean}, and
\textit{test-other} used for training, development, and testing, respectively.
Subsets tagged with \textit{other} are more challenging utterances from
speakers that yield higher WER as measured with previously built models. LS is
used for unsupervised representation pre"=training by ignoring its labels, and
can also be utilized to evaluate the performance of representation on ASR, phoneme recognition (PR),
phoneme classification (PC), and speaker identification (SID) tasks. Wall Street Journal (WSJ)~\parencite{paul_design_1992} is another
widely adopted, labeled corpus for pre"=training. Its labels can evaluate
performance for ASR, PR, PC, and SID. The original WSJ corpus contains 400 hours
of English read speech data, and today its \textit{si284} (81 hours),
\textit{dev93}, \textit{eval92} subsets are the most-used partitions for
unsupervised training, development, and test, respectively.  The \textit{si84}
(15 hours) partition is also used for training.

The speech community also utilizes multilingual corpora. These are often
large-scale, which facilitates pre"=training, but are also partially labeled for ASR
evaluation (PC and PR can be enabled via phone-level forced alignment). These
corpora include Common Voice (CV)~\parencite{ardila_common_2020}, Multilingual
LibriSpeech (MLS)~\parencite{pratap_mls_2020}, VoxPopuli 
(VP)~\parencite{wang_voxpopuli_2021}, and BABEL (BBL)~\parencite{gales_speech_2014}. CV is
an open-source, multi-language, growing dataset of voices containing 11k hours
of audio from 76 languages as of the date this review was written (Common Voice
corpus~7.0). Researchers usually use part of this for pre"=training (e.g., 7k
hours/60 languages in \parencite{babu_xlsr_2021} and 430 hours/29 languages in
\parencite{kawakami_learning_2020}) or evaluation. 
MLS derives content from read audiobooks of LibriVox and contains data in eight
European languages for a total of 50k hours of audio. VP comprises a total of 400k
hours of parliamentary speech from the European parliament in 23 European
languages.
The entire dataset~\parencite{babu_xlsr_2021} or a 24k-hour 
portion~\parencite{chen_unispeechsat_2021, chen_wavlm_2021} thereof has been used for pre"=training. BBL
consists of 1k hours of conversational telephone speech in 17 African and Asian
languages.

Several datasets, including GigaSpeech~\parencite{chen_gigaspeech_2021}, TED-LIUM~3
(TED3)~\parencite{hernandez_tedlium_2018}, TED-LIUM~2 (TED2)~\parencite{rousseau_tedlium_2012},
Switchboard (SWB)~\parencite{godfrey_switchboard_1992}, 
TIMIT~\parencite{garofolo_timit_1993}, and VoxLingua107 \parencite{valk_voxlingua107_2021}, are
labeled and conventionally used for evaluation, while their audio streams are
also aggregated to build diversified and large-scale corpora for unsupervised
pre"=training~\parencite{kawakami_learning_2020, song_speechxlnet_2020, babu_xlsr_2021}.
GigaSpeech is a multi-domain English ASR corpus with 33k hours of audio
collected from audiobooks, podcasts, and YouTube. A subset of 10k audio is
transcribed. TED2 comes with 118 hours of English speech extracted from
TED conference talks and its transcription for evaluating ASR. Its recordings
are clear but with some reverberation. TED3 is an extension of TED2 and
comprises 450 hours of talks. SWB is a 260-hour conversational speech
recognition dataset containing two-sided telephone conversations.
The TIMIT corpus was designed to provide read speech data and its word and
phone-level transcriptions for acoustic-phonetic studies. It contains recordings
in American English. Compared to the previous corpora labeled for ASR
evaluation, VoxLingua107 consists of 6.6k hours of audio in 107 languages and
is annotated for language identification. Beyond the original purpose of
evaluation, these corpora are also used in pre"=training to improve the
generalizability of learned representations.

For the purpose of pre"=training and evaluating Mandarin speech representations,
the authors of \parencite{jiang_improving_2019, jiang_further_2021} also compiled Open Mandarin, 
an open-source Mandarin dataset of 1.5k hours of speech from
the Linguistic Data Consortium (LDC) and
OpenSLR.\footnote{\url{https://openslr.org}} Open Mandarin consists of the HKUST
Mandarin Telephone Speech Corpus (HKUST, 200 hours of spontaneous 
speech, of which
168 hours of audio is used for pre"=training; the development and test sets are
excluded.)~\parencite{liu_hkust_2006}, AISHELL-1~\parencite{bu_aishell1_2017} (178 hours of
read speech),
aidatatang 200zh (200 hours, read speech)~\parencite{beijingdatatangtechnologycoltd_aidatatang_}, MAGICDATA
Mandarin Chinese Read Speech Corpus (755 hours, read speech)~\parencite{magicdatatechnologycoltd_magicdata_2019},
Free ST Chinese Mandarin Corpus (ST-CMDS, 100 hours, read speech)~\parencite{surfingtechcoltd_stcmds_},
and Primewords Chinese Corpus Set 1 (100 hours, read speech)~\parencite{primewordsinformationtechnologycoltd_primewords_2018}. 
Both HKUST and AISHELL-1 are labeled and are suitable for ASR evaluation.

@@

Besides the aforementioned datasets, conventional speech processing benchmarks
are also used to evaluate self"=supervised representations. Studies leverage Hub5,
DIRHA, and CHiME-5 to measure the efficacy of representations in ASR.
The Hub5 evaluation (LDC2002T43 and LDC2002S09, also referred to as the NIST 2000
Hub5 English evaluation set) contains 40 transcribed English telephone
conversations only for testing, where 20 are from conversations collected in
SWB studies but not released with the SWB dataset, and the rest are from CallHome
American English Speech (LDC97S42). DIRHA~\parencite{ravanelli_dirhaenglish_2015}, short for
Distant-speech Interaction for Robust Home Applications, is a database composed
of utterances sampled from WSJ, speech of keywords and commands, and
phonetically-rich sentences. These utterances are read by UK and US English
speakers and recorded with microphone arrays. CHiME-5~\parencite{barker_fifth_2018} is
a challenge that aims to advance robust ASR and presents a dataset of natural
conversational speech collected under a dinner party scenario with microphone
arrays. A team at Amazon Alexa also recorded and transcribed a corpus of 1k
hours of audio for model training and evaluation~\parencite{sadhu_wav2vecc_2021}.

@@

Last, \parencite{tagliasacchi_pretraining_2020} puts together five datasets 
(MUSAN~\parencite{snyder_musan_2015}, Bird Audio Detection \parencite{stowell_automatic_2019},
Speech Commands~\parencite{warden_speech_2018}, Spoken Language 
Identification~\parencite{oponowicz_spoken_2018}, and TUT Urban Acoustic Scenes 2018~\parencite{mesaros_detection_2018}) plus
an SID task built with the LS \textit{train-clean-100} subset to evaluate the
capability of representations on audio event detection.
\parencite{quitry_learning_2019} employs the NSynth dataset~\parencite{engel_neural_2017} on top
of the six for benchmarking. As many of the datasets are built for research in
audio processing, we here provide only a list of these datasets for reference.

\begin{table*}[t]
  \centering
  \scriptsize %footnotesize %small, scriptsize, tiny
  \caption[Summary of datasets used for pre"=training or evaluation of SSL techniques in the literature.]%
  {Summary of datasets used for pre"=training (denoted as PT) or
  evaluation (denoted as EV) of SSL techniques in the literature. The languages and
  sizes of the datasets are provided in columns 3 and 4. Column 5 lists the tasks each
  dataset is used to evaluate. Abbrevations are listed in \cref{footnote:table:datasets-abbrevations}.}
  \label{table:datasets}
  \resizebox*{0.99\textwidth}{!}{%
  {\renewcommand*\arraystretch{1.2}
  \begin{tabular}{llllll}
    \toprule
    Dataset & Purpose & Lang. & Size [hours] & Task & License \\
    \midrule
    LibriLight (LL) & PT & EN & 60k & - & MIT License \\ \hline
    AudioSet & PT & Multi & 2.5k & - & CC BY 4.0 \\ \hline %Bidir-CPC, Audio2Vec
    AVSpeech & PT & Multi & 3.1k & - & CC BY 4.0 \\ \hline %Bidir-CPC
    Fisher & PT & EN & 2k/1k \parencite{jiang_further_2021}  & - & Linguistic Data Consortium (LDC) \\ \hline % MPC

@@

    \multirow{2}{*}{Work} & \multirow{2}{*}{\makecell[l]{pre"=training\\ corpus}} & \multirow{2}{*}{Task} & \multicolumn{2}{c}{Dataset} & \multirow{2}{*}{Transfer} & \multirow{2}{*}{Fine-tuning labels used} \\ \cline{4-5}

@@

\addtocounter{footnote}{1}
\footnotetext{\label{footnote:table:method_data_setting}
  The \textbf{pre"=training corpus}, \textbf{Fine-tuning}, and
  \textbf{Test} columns list the datasets used in each work, and the \textbf{Task}
  column lists the tasks performed in the corresponding papers. 
  The \textbf{Transfer} column indicates whether the SSL technique is evaluated by its capability for
  transfer learning, i.e., different datasets are utilized for pre"=training and
  fine-tuning. The \textbf{Fine-tuning labels used} column summarizes the
  amount of labeled examples used in downstream fine-tuning.
}

@@

\addtocounter{footnote}{1}
\footnotetext{\label{footnote:AED-datasets}
The 6 AED datasets used in
\parencite{tagliasacchi_pretraining_2020} are MUSAN~\parencite{snyder_musan_2015}, Bird Audio
Detection~\parencite{stowell_automatic_2019}, Speech Commands~\parencite{warden_speech_2018},
Spoken Language Identification~\parencite{oponowicz_spoken_2018}, TUT Urban Acoustic
Scenes 2018~\parencite{mesaros_detection_2018} plus an SID task built with LS
\textit{train-clean-100}. In addition to the 6 datasets,
\parencite{quitry_learning_2019} use the NSynth dataset~\parencite{engel_neural_2017} for
evaluation.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:CPC-8k}
A collection of AudioSet, AVSpeech,
CV-dataset, LS, WSJ, TIMIT, Speech Accent Archive 
(SSA)~\parencite{weinberger_speech_2011}, TED3, and SWB. SSA is a growing annotated corpus of
English speech with various accents. Among the papers studied in this review, SSA
is used in \parencite{kawakami_learning_2020} only for pre"=training, and only 1 hour
of audio is utilized. Thus, we exclude it from our discussion in
\cref{section:benchmark}.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:low-resource}
A subset of the official training
split is sampled, usually to mimic low-resource learning conditions or to
quickly evaluate for training and testing on the same split but disjoint
subsets.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:APC-split}
Dataset split into training,
validation, and test subsets at a ratio of 8:1:1.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:91-split-dev}
Dataset split into training
and validation subsets at a ratio of 9:1.}
\addtocounter{footnote}{1}
\footnotetext{\label{footnote:91-split-test}
The dataset split into training
and test subsets at a ratio of 9:1.}

\subsection{Experiment settings for evaluating SSL techniques}
A common way to benchmark SSL techniques and show their efficacy is to
fine-tune a pre-trained SSL model for a supervised downstream task.
Depending on the corpora used in pre"=training and fine-tuning, techniques can
be benchmarked in terms of their capability to transfer knowledge across datasets
(i.e., using pre"=training corpora that differ from the fine-tuning ones), their
benefit when training with limited labeled examples (i.e., sampling a subset of
labeled examples for fine-tuning), or their improvement over a fully supervised
baseline (i.e., using the entire training split of downstream datasets for
fine-tuning). \cref{table:method_data_setting,table:method_data_setting_2} summarize experiment settings used in the
SSL literature, including the pre"=training corpora, downstream tasks and datasets,
and the amount of fine-tuning labels used, which indicates the targeted
benchmarking scenario as discussed above. Note that there are a variety of ways
to fine-tune pre-trained networks (e.g., fine-tune the entire network,
freeze certain layers during fine-tuning, and add various architectures of
prediction layers to pre-trained networks). We here omit
descriptions of these choices; readers can consult the
original publications for details.

As observed in \cref{table:method_data_setting,table:method_data_setting_2}, LS and WSJ are the most commonly used
pre"=training corpora. At the same time, we observe a
growing industry investment in pre"=training with larger datasets, e.g.,
CPC-8k (8k hours) for Bidir-CPC \parencite{kawakami_learning_2020}, LL (60k hours) for
CPC modified~\parencite{riviere_unsupervised_2020}, 
wav2vec 2.0~\parencite{baevski_wav2vec_2020}, and HuBERT~\parencite{hsu_hubert_2021}, Alexa internal
datasets (10k hours) for wav2vec-c~\parencite{sadhu_wav2vecc_2021}, Didi internal
datasets (10k hours) for MPC~\parencite{jiang_improving_2019, jiang_further_2021}, the
combination of Gigaspeech, VP-24k, and LL (94k hours in total) for
UniSpeech-SAT~\parencite{chen_unispeechsat_2021} and WavLM~\parencite{chen_wavlm_2021}, and
the combination of VP-400K, MLS, CV-dataset, VL and BBL (436k hours in total)
for XLS-R~\parencite{babu_xlsr_2021}. We expect this trend to continue with the growth
in available computing power. Most studies focuses on learning representations
for English, whereas Chinese~\parencite{jiang_improving_2019, jiang_further_2021} and
multilinguality~\parencite{kawakami_learning_2020, babu_xlsr_2021} are also gaining
attention. Compared to pre"=training, datasets used for fine-tuning are more
diverse and cover downstream tasks as varied as ASR, PR, PC, SID, AED,
Sentiment, ST, and LID. For benchmarking training scenarios covering full
supervision as well as limited resources, the amount of labeled examples used for
fine-tuning also varies from several minutes up to 1k hours. Recent
benchmarks such as SUPERB~\parencite{yang_superb_2021} that consolidate multiple 
downstream tasks have gained attention for evaluating SSL
methodologies~\parencite{chen_unispeechsat_2021, chen_wavlm_2021}. The goal of such benchmarks is
to provide a holistic evaluation of the performance of learned representations; 
we discuss these in detail in \cref{sec:benchmark}. With the increasing
popularity of SSL research, we expect future experiment settings to proliferate
and cover more languages, downstream tasks, and pre"=training/fine-tuning
datasets.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{paper_review/ls-test-clean-v2.pdf}
\caption[SSL performance for ASR evaluated on
LS \textit{test-clean}.]{SSL performance on ASR WER (vertical axis) evaluated with
LS \textit{test-clean} split. Techniques are sorted based on the number of
model parameters along the horizontal axis. Markers in blue correspond to models initialized with various SSL
techniques and then fine-tuned using 960, 100, 10, 1 hour(s), and 10 minutes
respectively. The 960-hour training set is the aggregation of
\textit{train-clean-100}, \textit{train-clean-360}, and
\textit{train-other-500} splits. The 100-, 10-, 1-hour, and 10-minute sets
leverage \textit{train-clean-100} or its sampling, except for Bidir-CPC, which
samples 10\% of the training examples from the entire 960-hour corpus. For simplicity,
several SSL techniques are appended with suffixes \textit{B}, \textit{L},
\textit{XL}, or \textit{XXL} indicating the \textit{Base}, \textit{Large},
\textit{X-Large}, or \textit{XX-Large} variants specified in the original
publication. We also compare with baselines including the log mel filterbank (fBANK) and semi"=supervised, self-training
approaches (iterative pseudo labeling (IPL)~\parencite{xu_iterative_2020}, 
slimIPL~\parencite{likhomanenko_slimipl_2021}, noisy student~\parencite{park_improved_2020}). These approaches are visualized in black. Also, note that the current state of the art---conformer XXL + noisy student~\parencite{zhang_pushing_2020}---is a combination of self-training and SSL techniques. Given the
diversity of the listed methods in experiment settings (e.g., pre"=training corpora
and objectives, whether a language model is used in decoding, whether model
parameters are frozen in fine-tuning), readers should be careful that the superiority
of methods cannot be decided only based on lower WER numbers.}
\label{fig:asr_result_no_limit}
\end{figure*}
